Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

\item We present different variants of trend measures that consider noiseless data as well as noisy and small non-informative changes.

\item We introduce the conditional trend plot, a new graphical method for assessing local trends.

\item We introduce bootstrap methods for calculating confidence intervals. Confidence intervals for the measurements from the previous sections.

@@

\item We apply trend evaluation to three different applications: Measurement, nowcasting and prediction data.

\item The source code for the replication of the results of our study as well as a ready-to-use code for trendability detection are available in our public repository at [Link will be inserted] available.
\end{itemize}

The remainder of this paper is structured as follows. 
In Section \ref{sec:trending}, we formalize the concept of trending independently of the application domain and investigate quantification approaches for noise-free and noisy data. 
In particular, we introduce a new graphical method for evaluating trending, the conditional trending plot, which can represent the simultaneous evaluation of different intervals and asymmetries. 
Bootstrap methods for calculating confidence intervals for trending measures are also presented. 
In Section \ref{sec:application}, we show the results of applying our method to several practical examples from measurement, forecasting and nowcasting. 
We conclude our paper with the last section.

>>>>

\item We present different variants of trending measures that consider noiseless data as well as noisy and small non-informative changes.

\item We introduce the conditional trending plot, a new graphical method for assessing local trends.

\item We introduce bootstrap methods for calculating  confidence intervals for the presented treding ratios.

@@

\item We apply trending evaluation to three different applications: Measurement, nowcasting and prediction data.

\item We provide a ready-to-use code for trending detection. The code and the source code to replicate the results of our study are available in our public repository at ... .
\end{itemize}

The remainder of this paper is structured as follows. 
In Section \ref{sec:trending}, we formalize the concept of trending independently of the application domain and investigate quantification approaches for noise-free and noisy data. Noisy data refers to data where noise or unsystematic effects are present in the true values or predictions.
In particular, we introduce a new graphical method for evaluating trending, the conditional trending plot, which can represent the simultaneous evaluation of different intervals and asymmetries. 
Bootstrap methods for calculating confidence intervals for trending measures are also presented. 
In Section \ref{sec:application}, we show the results of applying our method to several practical examples from measurement, forecasting and nowcasting. 
We conclude our paper with the last section.
